Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-03 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
Texto añadido para XYZ

  \item {\bf Evolutionary Algorithm} 
  The EA algorithm interacts with the data model. The EA could also be done with the help of
  humans, for instance in the XY project \cite{de2013unplugging} artists actually painted
  the solutions of the new population.  
\end{itemize}

@@

\section{Case Study: XYZ-Unplugged}
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/interfaceXYZ.png}
    \caption{User interface of the XYZ application.}
    \label{fig:xyz}
\end{figure}

>>>>

  \item {\bf Evolutionary Algorithm} 
  The EA algorithm interacts with the data model. The EA could also be run with the help of
  humans, for instance in the XY project \cite{de2013unplugging} artists actually painted
  the solutions of the new population and applied every genetic operator.
\end{itemize}

@@

\section{Case Study: XYZ-Unplugged}

XYZ is a collective artwork generated by means of the Unplugged version of the Evolutionary Algorithm.  While in the previous cases software tools are in charge of running the EA and users collaborate evaluating fitness quality, the software tool in XYZ is only in charge of storing digital versions of the works produced by the team of artists, who are really in charge of applying every step of the evolutionary algorithm.

Thus, the main difference between the standard IEC and the Unplugged EA, is that in the latest, every genetic operation as well as the general evolutionary loop is in charge of human beings.  Thus the team of artists are in charge of:  (i) setting up the initial population by selecting well known works from the history of arts;  (ii) each of the artists selects every generation two works from the previous one, and produce a new painting by applying any kind of crossover and mutation he may consider (iii) the process repeats for the number of generations initially decided, so that at the end, a collective artwork has been produced including as many paintings per generation, as artists are participating in the experiment.

Artists resort to i-EvoSpace as the tool allowing them to store the paintings, deciding their preferred ones from the previous generation, as well as describing the reasons for their selections, mutation and crossover operations applied.  The tool is also in charge of generating statistics, computing \textit{elitism}, thus adding the most selected work to the next generation, etc.

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/interfaceXYZ.png}
    \caption{User interface of the XYZ application.}
    \label{fig:xyz}
\end{figure}
